\documentclass[11pt,letterpaper]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[parfill]{parskip}
\usepackage{lmodern}
\usepackage{array}

% Adjust margins to be tighter
\usepackage[margin=0.5in]{geometry}

% Adjust section formats - reduced spacing
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{6pt}{4pt}

% Reduce itemize spacing significantly
\setlist[itemize]{leftmargin=*, topsep=-2pt, itemsep=-2pt, parsep=0pt}

% Define a vertical bar command with proper spacing
\newcommand{\divbar}{\ensuremath{\:}\textbar\ensuremath{\:}}

% Define a semi-bold text command
\newcommand{\semibold}[1]{{\fontseries{sb}\selectfont #1}}

% Command for job entries with adjusted spacing
\newcommand{\jobentry}[4]{
    {\noindent\textbf{#1}\hfill#2}\\[0.3em] % More space between company and role
    {\noindent\semibold{#3}\hfill#4}\\[-0.5em] % Negative space to pull up bullet points
}

\begin{document}

{\centering\Large\textbf{Michael Cohen}\par}
\vspace{-0.3em}
{\centering New York, NY \hspace{2em} (305) 733-5490 \hspace{2em} \href{mailto:micohen13@gmail.com}{micohen13@gmail.com} \hspace{2em} \href{https://michaelcohen.io}{michaelcohen.io}\par}
\vspace{0.2em}

\section{Work Experience}

\jobentry{Anthropic}{Aug '24 -- Present}{Member of Technical Staff \divbar API Team}{}
\begin{itemize}
    \item Developing new product features and improvements for Anthropic's API.
\end{itemize}

\jobentry{OpenSea}{Aug '22 -- Dec '23}{Engineering Manager \divbar Creator Team}{}
\begin{itemize}
    \item Hired and managed 6 engineers (FE + BE) focused on creator products/tools.
    \item Led team in developing Primary Drops, a \$30M+ GMV NFT creation platform, grew from 0\% to $\sim$30\% market share.
    \item Shipped Creator Studio, a one-stop shop, no-code solution for creators to build \& manage 16+ million NFTs created across 11K collections to date.
    \item Shipped new highly customizable collection landing pages, with rich storytelling for creators.
    \item Collaborated with BD, marketing, ops, legal, and finance to secure 50+ high-value partnerships, ensuring seamless product launches resulting in \$30M+ in GMV growth.
\end{itemize}

\jobentry{OpenSea}{Jun '21 -- Aug '22}{Senior Software Engineer \divbar Platform Team}{}
\begin{itemize}
    \item Enhanced OpenSea's platform by introducing scalable architecture improvements; directly contributed to a 50\% increase in uptime during a period of rapid growth and high user demand.
    \item Led the scaling, migration, and documentation rewrite of the public REST API, introduced a new Websocket API, and integrated advanced queuing systems for robust scalability.
    \item Developed a robust spam detection algorithm for NFT mints, cutting down fake NFT listings by 75\%, and successfully integrated Solana blockchain, boosting transaction efficiency and reliability within the marketplace.
\end{itemize}

\jobentry{Amazon}{Mar '18 -- Jun '21}{Software Engineer}{}
\begin{itemize}
    \item Led development of Data Lifecycle Manager for AWS Backup Service (\$2.9B revenue in 2017), automating backup policies for data stored on EBS volumes.
    \item Built full-stack features for iOS Creator app and led FireTV project, transforming Amazon Shopping app into a livestream-centric experience.
    \item Implemented gamification features for Amazon Live platform, growing creator base from under 2K to over 15K creators.
\end{itemize}

\section{Education}
\jobentry{University of Florida}{December 2017}{B.S. in Computer Science Engineering}{}

\section{Skills}
\begin{itemize}
    \item \textbf{Languages \& Frameworks:} Python, Java, TypeScript, React, NodeJS, Elixir, Solidity, Go
    \item \textbf{Expertise:} Distributed Systems, Backend Development, Frontend Development, Full Stack Web Development, Mobile Applications (iOS / Android), Cloud \& Serverless Architecture, Smart Contract Development
\end{itemize}

\end{document}
